### 2005-01-13 Documentation/Paper/paper.tex
last changes am Manual
Ref. report changes incorporated

\vspace*{-3.cm}
\begin{flushright}
TUM-HEP-5XX/04\\
%hep-ph/
\end{flushright}

@@

\begin{abstract}
We present the \GLOBES\ (``General Long Baseline Experiment Simulator'')
software package, which allows the simulation of long-baseline and reactor
neutrino oscillation experiments. One part of the software is the
abstract experiment definition language to define experiments with
beam and full detector descriptions as accurate as possible. Many systematics options are provided, such as normalization and energy
calibration errors, or the choice between spectral or total rate 
information. For the 
definition of experiments, a new transparent building block concept is 
introduced. In addition, an additional program provides the possibility 
to develop and test new experiment definitions quickly.
%
Another
part of \GLOBES\ is the user's interface, which provides probability, rate, 
and $\Delta \chi^2$ information for a given experiment or any
combination of up to 32 experiments in C. Especially, the
$\Delta \chi^2$ functions allow a simulation with statistics only,
systematics, correlations, and degeneracies. In particular, \GLOBES\
can handle the full multi-parameter correlation among the oscillation
parameters, external input, and matter density uncertainties. 
\end{abstract}

@@

\section{Use of package}

@@

The installation of \GLOBES\ is highly automated by the use of the
Autotools family and follows the usual procedures. By default
a shared library {\tt libglobes.so} is installed, but 
a static version is available, too. In addition, an executable named {\tt globes} is installed. It is another possibility to install \GLOBES\ without
root privilege into a user's home directory. During the automatic
configuration process also an example Makefile is produced which can
serve as a template for compiling and linking own applications against
{\tt libglobes.so}. This Makefile can be used to directly compile and
link the examples
from the manual.

>>>>

\vspace*{-3.cm}
\begin{flushright}
TUM-HEP-553/04\\
%hep-ph/
\end{flushright}

@@

\begin{abstract}
We present the \GLOBES\ (``General Long Baseline Experiment Simulator'')
software package, which allows the simulation of long-baseline and reactor
neutrino oscillation experiments. One part of the software is the
abstract experiment definition language to define experiments with
beam and full detector descriptions as accurately as possible. Many systematics options are provided, such as normalization and energy
calibration errors, or the choice between spectral or total rate
information. For the
definition of experiments, a new transparent building block concept is
introduced. In addition, an additional program provides the possibility
to develop and test new experiment definitions quickly.
%
Another
part of \GLOBES\ is the user's interface, which provides probability, rate,
and $\Delta \chi^2$ information for a given experiment or any
combination of up to 32 experiments in C. Especially, the
$\Delta \chi^2$ functions allow a simulation with statistics only,
systematics, correlations, and degeneracies. In particular, \GLOBES\
can handle the full multi-parameter correlation among the oscillation
parameters, external input, and matter density uncertainties.
\end{abstract}

@@

\section{Use of the package}

@@

The installation of \GLOBES\ is highly automated by the use of the
Autotools family and follows the usual procedures. By default
a shared library {\tt libglobes.so} is installed, but 
a static version is available, too. In addition, an executable named {\tt globes} is installed. It possible to install \GLOBES\ without
root privilege into a user's home directory. During the automatic
configuration process also an example Makefile is produced which can
serve as a template for compiling and linking own applications against
{\tt libglobes.so}. This Makefile can be used to directly compile and
link the examples
from the manual.
